---
title: 'STOR 455 Group Project (Due 5pm on November 24th)'
subtitle: "Old Geezers"
output:
  pdf_document: default
---

Hunter Buresh (), Alex Georgiev (730483404), Zach Richardson ()

# The Prediction (Required)
Our prediction of the cumulative domestic box office of "The Marvels" by December 8, 2023 is ...

# Summary of Justification (Required) 


# Data (Required)
We obtained the dataset from: <FILL IN URL HERE>.
### Preview of dataset
``` {r}
data <- read.csv("marveldata.csv", quote="'")
summary(data)
head(data, 5)

# We don't need the id, distributor, title, or date columns
modelData <- subset(data, select = -c(id, distributer, title, date))
summary(modelData)
```


# Analysis (Required)
We noticed that the opening gross for The Marvels was only $46 million. Looking at the distrbution of the opening gross of other Marvel movies shows that The Marvels has the lowest opening gross out of all the movies in the dataset.
### Distribution of opening gross
``` {r}
openGrossMil <- data$opengross/1000000
summary(openGrossMil)
```

### Full model
``` {r}
# Fit a model with all data
fullModel = lm(totalgross~opengross, data=modelData)
summary(fullModel)

# Plot regression line
plot(totalgross~opengross, data=modelData)
abline(fullModel)
```

### Model with low opening gross
``` {r}
# Get data with opening gross < 100 mil
lowOpeners = subset(modelData, opengross<=100000000)

# Fit model with low openers
lowOpenModel = lm(totalgross~opengross, data=lowOpeners)
summary(lowOpenModel)

# Plot regression line
plot(totalgross~opengross, data=lowOpeners)
abline(lowOpenModel)
```

### Model with only Fall releases
``` {r}
# Only take movies that had fall releases
fallData = subset(modelData, season=="Fall")
summary(fallData)
head(modelData)

# Fit model with fall releases
fallModel = lm(totalgross~opengross, data=fallData)
summary(fallModel)

# Plot regression line
plot(totalgross~opengross, data=fallData)
abline(fallModel)
```

### Table with prediction from all models
``` {r}
# Get The Marvels opening gross
theMarvelsOpenGross = data.frame(opengross=(subset(data, title=="The Marvels"))$opengross)

# Predictions for each model
fullPred = predict(fullModel, newdata = theMarvelsOpenGross)
lowOpenPred = predict(lowOpenModel, newdata = theMarvelsOpenGross)
fallPred = predict(fallModel, newdata = theMarvelsOpenGross)

# Create a data frame for the table
predictionTable <- data.frame(
  FullModel = fullPred,
  LowOpenModel = lowOpenPred,
  FallModel = fallPred
)

# Display the table
print(predictionTable)
```


## Predict only with daily earnings
``` {r}
# Convert table from website into dataframe
dailyEarnings <- data.frame(
  Date = c("Nov 20", "Nov 19", "Nov 18", "Nov 17", "Nov 16", "Nov 15", "Nov 14", "Nov 13", "Nov 12", "Nov 11", "Nov 10"),
  Day = c("Monday", "Sunday", "Saturday", "Friday", "Thursday", "Wednesday", "Tuesday", "Monday", "Sunday", "Saturday", "Friday"),
  Rank = c(4, 3, 3, 4, 1, 1, 1, 1, 1, 1, 1),
  Revenue = c(1137196, 2910248, 4453682, 2756659, 1251387, 1789239, 3300946, 2372375, 9247703, 15260052, 21603104),
  Change_Daily = c("-60.9%", "-34.7%", "+61.6%", "+120.3%", "-30.1%", "-45.8%", "+39.1%", "-74.3%", "-39.4%", "-29.4%", "-"),
  Change_LastWeek = c("-52.1%", "-68.5%", "-70.8%", "-87.2%", "-", "-", "-", "-", "-", "-", "-"),
  Theaters = c(4030, 4030, 4030, 4030, 4030, 4030, 4030, 4030, 4030, 4030, 4030),
  Avg = c(282, 722, 1105, 684, 310, 443, 819, 588, 2294, 3786, 5360),
  TotalRevenue = c(66082591, 64945395, 62035147, 57581465, 54824806, 53573419, 51784180, 48483234, 46110859, 36863156, 21603104),
  Week = c(11, 10, 9, 8, 7, 6, 5, 4, 3, 2, 1)
)

# Print the data frame
print(rowList)

# Preview data
summary(dailyEarnings)
head(dailyEarnings)
```

### SLR based on earnings since Nov 12
``` {r}
# Data that only contains Nov 12 and later
sinceNov12 = subset(dailyEarnings, (Date != "Nov 10") & (Date != "Nov 11")) 

# Add column that represents days since Nov 12
sinceNov12$DaysAfterOpeningWknd <- c(8, 7, 6, 5, 4, 3, 2, 1, 0)

# Show data
summary(sinceNov12)
sinceNov12

# Fit model passed on days since opening weekend
sinceNov12Model = lm(TotalRevenue~DaysAfterOpeningWknd, data=sinceNov12)

# Summarize model
summary(sinceNov12Model)

# Convert to millions for easier viewing
plotData = sinceNov12
plotData$TotalRevenue = plotData$TotalRevenue / 1000000

# Plot regression line
milModel = lm(TotalRevenue~DaysAfterOpeningWknd, data=plotData)
plot(TotalRevenue~DaysAfterOpeningWknd, data=plotData, yaxp=c(40,70,5), ylim=c(40, 70),
     main="Revenue Since Opening Weekend", xlab="Days Since Opening Weekend", ylab="Total Revenue")
abline(milModel)
```

