---
title: 'STOR 455 Group Project (Due 5pm on November 24th)'
subtitle: "Old Geezers"
output:
  pdf_document: default
---

Hunter Buresh (), Alex Georgiev (730483404), Zach Richardson ()

# The Prediction (Required)
Our prediction of the cumulative domestic box office of "The Marvels" by December 8, 2023 is ...

# Summary of Justification (Required) 


# Data (Required)
We obtained the dataset from: <FILL IN URL HERE>.
### Preview of dataset
``` {r}
data <- read.csv("marveldata.csv", quote="'")
summary(data)
head(data, 5)

# We don't need the id, distributor, title, or date columns
modelData <- subset(data, select = -c(id, distributer, title, date))
summary(modelData)
```


# Analysis (Required)
We noticed that the opening gross for The Marvels was only $46 million. Looking at the distrbution of the opening gross of other Marvel movies shows that The Marvels has the lowest opening gross out of all the movies in the dataset.
### Distribution of opening gross
``` {r}
openGrossMil <- data$opengross/1000000
summary(openGrossMil)
```

### Full model
``` {r}
# Fit a model with all data
fullModel = lm(totalgross~opengross, data=modelData)
summary(fullModel)

# Plot regression line
plot(totalgross~opengross, data=modelData)
abline(fullModel)
```

### Model with low opening gross
``` {r}
# Get data with opening gross < 100 mil
lowOpeners = subset(modelData, opengross<=100000000)

# Fit model with low openers
lowOpenModel = lm(totalgross~opengross, data=lowOpeners)
summary(lowOpenModel)

# Plot regression line
plot(totalgross~opengross, data=lowOpeners)
abline(lowOpenModel)
```

### Model with only Fall releases
``` {r}
# Only take movies that had fall releases
fallData = subset(modelData, season=="Fall")
summary(fallData)
head(modelData)

# Fit model with fall releases
fallModel = lm(totalgross~opengross, data=fallData)
summary(fallModel)

# Plot regression line
plot(totalgross~opengross, data=fallData)
abline(fallModel)
```

### Table with prediction from all models
``` {r}
# Get The Marvels opening gross
theMarvelsOpenGross = data.frame(opengross=(subset(data, title=="The Marvels"))$opengross)

# Predictions for each model
fullPred = predict(fullModel, newdata = theMarvelsOpenGross)
lowOpenPred = predict(lowOpenModel, newdata = theMarvelsOpenGross)
fallPred = predict(fallModel, newdata = theMarvelsOpenGross)

# Create a data frame for the table
predictionTable <- data.frame(
  FullModel = fullPred,
  LowOpenModel = lowOpenPred,
  FallModel = fallPred
)

# Display the table
print(predictionTable)
```